%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


    %---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {Amazon} % Organization
    {Hyderabad, India} % Location
    {Feb. 2019 - Present} % Date(s)
    { \begin{cvitems} % Description(s) of tasks/responsibilities
            \item{Worked on migration of services from monolithic architecture with on-prem hosting to micro-services architecture hosted in AWS} % 6 commands only out of 14 and 14/16
            \item {Rearchitected  service code to modularize components reducing the time required for migration by 2 weeks.}
            \item {Revamped the testing infrastructure improving the overall reliability of the system and improving developer experience and code stability with automated unit tests, integration tests and regression testing.}  %unit8_t compression in lib
            \item {Mentored junior members of the team. This included helping them on-board to the codebase and Amazon ecosystem along with design patterns, code reviews and development best practices.}    
            \item {Improved efficiency by automating various manual tasks saving 0.5 hour of developer time per day. Updated run-books, improved documentation and published coding standards and guidelines for uniformity and enhanced developer productivity.}  %(restart in 5,6 minutes to no restarts )
        \end{cvitems}
    }



	%---------------------------------------------------------
	\cventry
	{Software Engineer} % Job title
	{PicoStone} % Organization
	{Mumbai, India} % Location
	{Mar. 2017 - Aug. 2018} % Date(s)
	{ \begin{cvitems} % Description(s) of tasks/responsibilities
	\item{Used semi-supervised learning to train AC remotes and designed an algorithm for the same. Sped up the learning process by 62.5\% and reduced the data overhead by 87.5\%.} % 6 commands only out of 14 and 14/16
      \item {Implemented secure Over-The-Air feature in the underlying firmware and created a dashboard for controlling firmware updates, viewing current status and handling errors. Successfully performed over 1000+ client devices with an achieved 99.99\% reliability.}
      \item {Led a team of 3 people who designed and developed products called Polar and IR Stone based on freeRTOS with avg 50\% data compression.}  %unit8_t compression in lib
      \item {Refactored embedded code by migrating it into libraries to make it reusable and scalable. Optimized performance and improved reliability and availability of the device by avg 99.99\%.}  %(restart in 5,6 minutes to no restarts )
      \item {Managed the deployment and development of server (working in a team of 2) and embedded system firmware in testing and production environments. Used proxy to distribute server load.}
     \end{cvitems}
  }


	%---------------------------------------------------------
	\cventry
	{Developer Intern} % Job title
	{Shaastr } % Organization
	{Mumbai, India} % Location
	{May. 2015 - Jul. 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented backend registration of user with multiple login types supported (google, facebook and email), privilege based user control (student,teacher or institute), backend admin panel and database implementation.}
			\item {Designed a cron utility to schedule tasks in real time and deployed it on amazon elastic compute cloud (EC2).}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}